---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swan

<!-- badges: start -->
<!-- badges: end -->

The goal of swan is to estimate Sleep-wear, Wake-wear, and Non-wear ('SWaN') in wrist-worn accelerometry.  The `swan` packagge creates a specific 'conda' environment 
and wrappers apply this to rawdata (sub-second) to get an estimate of non-wear in 30 second blocks. It wraps the Python implementation <https://github.com/binodthapachhetry/SWaN> published in 'Detecting Sleep and Nonwear in 24-h Wrist Accelerometer Data from the National Health and Nutrition Examination Survey' <https://doi.org/10.1249%2FMSS.0000000000002973>.

## Installation

You can install the development version of `swan` like so:

``` r
remotes::install_github("jhuwit/swan")
```

## Example

```{r example}
library(swan)
unset_reticulate_python()
use_swan_condaenv()
file = system.file("extdata", "73557_subset.csv.gz", package = "swan")
df = readr::read_csv(file)
readr::stop_for_problems(df)
out = swan(df, sampling_rate = 80L)
head(out$first_pass)
head(out$second_pass)
out$second_pass %>% dplyr::count(prediction)
## basic example code
```
